### 2017-09-22 monograph/thesis/chapters/implementation.tex
Renamed newtcolorbox from myquote to bluebox
Partially translated monograph/thesis/chapters/implementation.tex

    Such software ideia may to a certain extent may continue a branch of the of
    the student `Lucas Boppre Niehues'\s graduation thesis, oriented by the
    Professor `Olinto José Varela Furtado', entitled 'Study and Creating a
    Structured Code Editor' defended in 2013/1 \cite{structuredEditorStudy}.
    While reading its work, the following section that links to one of the
    proposals of this work, in the chapter: `8.1.2 \brazilword{Separação de
    formato de exibição e de saída}':

    \medskip
    \begin{citacao}
    As formas que o código é exibido ao usuário e que ele é salvo em disco são controladas
    por arquivos de configuração distintos. O arquivo `theme.ini' contém, entre outras
    configurações, informações de como serializar a árvore sintática.
    \end{citacao}

    \vspace{-5mm}
    ...
    \begin{citacao}
    A configuração de formato de saída é dada da mesma forma, mas em um arquivo
    separado, chamado `output\_format.ini'. A decisão desta separação foi em vista de equipes
    de programadores que queiram utilizar uma convenção única para os arquivos salvos,
    mas manter a exibição a escolha de cada um. Assim os integrantes desta equipe podem
    compartilhar os seus arquivos `output\_format.ini' enquanto personalizam o arquivo
    `theme.ini' a seu gosto.
    \end{citacao}

    Com base nisso, pode-se pensar na escrita de plugins para editores de texto/IDEs comuns como
    Sublime Text. Assim ao carregar o arquivo do disco, este plugin chama o formatter e faz a
    formatação de acordo com as configurações de exibição para o usuário. Após isso, quando o
    usuário for salvar o arquivo, o arquivo com a formatação original é devolvido.

    Para auxilar nesse processo, um módulo de autoconfiguração é de grande ajuda. Ele detecta como o
    source code está formatado e cria arquivos de configuração para ele. Assim ao salvar o arquivo,
    automaticamente ele é salvo no formato que ele foi lido. Então temos o mesmo beneficio de
    editores estruturados, como proposto trabalho de `Lucas Boppre Niehues'. De inicio podemos
    pensar com os seguinte objetivo/ideia para um TCC:

    \medskip
    \begin{myquote}
    \begin{enumerate}[nolistsep]
        \item Criar um formatador de fácil configuração e expansão para as linguagens de
              programação que existem e que irão existir.
    \end{enumerate}
    \end{myquote}

\subsection{Problema}

    O problema proposto a se resolver é criar um Beautifier Universal. Os softwares atuais são
    limitados a um conjunto similar, ou mesmo à uma única linguagem, e além de muitos, serem
    limitados ao que eles podem fazer por você ao processar/formatar o código. \cite{universalCodeFormatter}

    Language-agnostic pretty-printing through machine learning (uh, like, is this possible? YES, apparently). By Terence Parr (primary developer), Fangzhou (Morgan) Zhang (help with initial development), Jurgen Vinju (co-author of academic paper, help with empirical results and algorithm discussions).
    \url{https://github.com/antlr/codebuff}

    To every developer in this world, the closest thing to their heart is the text editor of their
    choice. Over the last few years many new text editors has come into the market in both free and
    paid model, but unfortunately not all of them were able to make a real dent on the developer
    community. I remember in my college days we uses to use Notepad++ as our beloved text editor, as
    at that point of time it was one of the popular and free text editor with a lot of features for
    coding. But as time goes on, the entire development community started to lean towards sublime
    text since it’s launch.
    \url{https://www.isaumya.com/sublime-text-vs-atom-which-one-i-prefer-most-and-why/}

    As a developer, your code editor is one of the most important parts of your setup. It can save
    your wrists and fingers from repetitive strain injuries. It can save your eyes from going blind
    after a coding marathon.
    \url{https://hackernoon.com/virtualstudio-code-the-editor-i-didnt-think-i-needed-16970c8356d5}

    VS Code is an Editor while VS is an IDE.
    \url{https://stackoverflow.com/questions/30527522/what-are-the-differences-between-visual-studio-code-and-visual-studio}

    Implement tabstops with white space align.

    The solution - move tabstops to fit the text between them and align them with matching tabstops
    on adjacent lines.
    \url{http://nickgravgaard.com/elastic-tabstops/}
    \url{https://forum.sublimetext.com/t/elastic-tabs/128}

    What is the difference between VS Code and VS Community?
    Visual Studio Code is a streamlined code editor with support for development operations like
    debugging, task running and version control. It aims to provide just the tools a developer needs
    for a quick code-build-debug cycle and leaves more complex workflows to fuller featured IDEs.
    For more details about the goals of VS Code, see Why VS Code.
    \url{https://code.visualstudio.com/docs/supporting/faq#_licensing}

    Reg Replace is a plugin for Sublime Text 2 that allows the creating of commands consisting of
    sequences of find and replace instructions.
    \url{https://forum.sublimetext.com/t/regreplace-plugin/3810}

    The main reason I moved was that I find that it’s much slower, the simple things like opening a
    new window for a project should be instantaneous and sadly it’s far from it. As I've said before
    it's all about personal preference, I've gone back to Sublime but Adam for example is sticking
    with it...
    \url{http://engageinteractive.co.uk/blog/atom-review}

    Logo abaixo há algumas regras de formatação básica encontrados no serviço online
    \url{http://prettyprinter.de/} acessado em março/2017:

    \medskip
    \begin{myquote}
    \begin{enumerate}[nolistsep]
        \item Add new lines after `\{' and before `\}
        \item Add new lines before `\{'
        \item Remove empty lines
        \item Add comment lines before function
        \item Add new lines after `;'
        \item Add new lines after `\}'
        \item Remove new lines
        \item Reduce whitespace
        \item Put the code again in the input box above after submit
    \end{enumerate}
    \end{myquote}

    A partir deste ponto, apresenta-se um esboço sobre o problema, soluções, informações como
    porquês de se querer fazer um software assim, ou ainda de querer-se o beautifying:

@@

        Motivação: Existem muitas ferramentas distintas, por vezes pagas, e
        dificilmente completas. \cite{universalCodeFormatter}

        Muitas linguagens de programação existem, assim sempre ter fazer um software Beautifier para
        cada uma delas é muito trabalhoso \cite{universalCodeFormatter}. Mas a abordagem para um Beautifier
        Universal proposta nesse trabalho, permite que facilmente novas linguagens sejam
        adicionadas, sendo elas completamente diferentes das anteriores, ou similares. No caso de
        similaridades, basta reutilizar as estruturas de configuração das linguagens já existentes.

        Preocupa-se de fazer um Beautifier para cada uma delas por que programadores atualmente
        trabalham diariamente com varias dessas linguagens, e elas não são similares. Assim precisa-
        se configurar vários beautifiers para fazer a formatação. Isso é um problema por que,
        somente alguns beautifiers são mais completos, e toda vez que precisa-se fazer uma alteração
        no estilo de formatação, precisa-se propagar manualmente a mesma mudança ao longo de vários
        arquivos de configuração de programas distintos, o que é ruim pois toma ao usuário muito
        tempo de aprender a lidar com várias e muito diferentes tipos de configurações.
        \cite{Schweitzer}

        No caso do Beautifier que propõem-se, uma mudança no estilo é propagada para todas as
        linguagens. E caso queira-se deixar alguma linguagem fora da regra, basta remover ela da
        lista ao qual esse bloco da configuração se aplica, e `a)' deixar ela de fora assim nenhuma
        mudança é aplicada a ela. Ou `b)' criar um novo bloco que inclua somente ela com a
        configuração desejada.

        A seguir, temos algumas frases sobre o assunto:

        \begin{citacao}
        % \setlength{\itemindent}{5pt}
        One of absolute worst, worst methods of teamicide for software developers is to engage
        in these kinds of passive-aggressive formatting wars. I know because I've been there.
        They destroy peer relationships, and depending on the type of formatting, can also damage
        your ability to effectively compare revisions in source control, which is really scary.
        I can't even imagine how bad it would get if the lead was guilty of this behavior. That's
        leading by example, all right. Bad example. \cite{Atwood}
        \end{citacao}
        \vspace{-5mm}
        ...
        \begin{citacao}
        So yes, absurd as it may sound, fighting over whitespace characters and other seemingly
        trivial issues of code layout is actually justified. Within reason of course -- when done
        openly, in a fair and concensus building way, and without stabbing your teammates in the
        face along the way. \cite{Atwood}
        \end{citacao}

        \begin{citacao}
        I'd say there are two main reasons to enforce a single code format in a project. First has
        to do with version control: with everybody formatting the code identically, all changes in
        the files are guaranteed to be meaningful. No more just adding or removing a space here or
        there, let alone reformatting an entire file as a `side effect' of actually changing just a
        line or two. \cite{Geukens}
        \end{citacao}

@@

\subsubsection{Pontos}

@@

    Softwares existentes e similares:

    \medskip
    \begin{myquote}
    \begin{enumerate}[leftmargin=*]

        CodeBeautify is an online code beautifier which allows you to beautify your source code:
        \url{http://codebeautify.org/}.

        A universal code formatter, written in Dart: \url{https://pub.dartlang.org/packages/unifmt}.

        Google-java-format is a program that reformats Java source code to comply with Google Java
        Style: \url{https://github.com/google/google-java-format}.

        CodeFormatter is a Sublime Text 2/3 plugin that supports format (beautify) source code.
        \url{https://github.com/akalongman/sublimetext-codeformatter} and
        \url{https://github.com/aukaost/SublimePrettyYAML}

        UniversalIndentGUI offers a live preview for setting the parameters of nearly any indenter.
        You change the value of a parameter and directly see how your reformatted code will look
        like. Save your beauty looking code or create an anywhere usable batch/shell script to
        reformat whole directories or just one file even out of the editor of your choice that
        supports external tool calls: \url{http://universalindent.sourceforge.net/} and
        \url{https://github.com/danblakemore/universal-indent-gui}.

    \end{enumerate}
    \end{myquote}

@@

    % How to add `parsep` to `itemsep` and set `parsep` to 0pt, when declaring my list?
    % https://tex.stackexchange.com/questions/366904/how-to-add-parsep-to-itemsep-and-set-parsep-to-0pt-when-declaring-my-list
    \begin{sloppypar}
    \begin{myquote}\RaggedRight
    \begin{enumerate}[leftmargin=*,parsep=0pt]

>>>>

    Such software ideia may to a certain extent may continue a branch of the of
    the student `Lucas Boppre Niehues'\s graduation thesis, oriented by the
    Professor `Olinto José Varela Furtado', entitled 'Study and Creating a
    Structured Code Editor' defended in 2013/1 \cite{structuredEditorStudy}.
    While reading its work, the following section that links to one of the
    proposals of this work, in the chapter: `8.1.2 Separation of display and
    output format\footnote{Translation of: \brazilword{Separação de formato de
    exibição e de saída}}':

    \begin{citacao}
    The ways that code is displayed to the user and that it is saved to disk are
    controlled by different configuration files. The `theme.ini' file contains,
    among other settings, information on how to serialize the syntax tree.
    \cite[our translation]{structuredEditorStudy} \footnote{\brazilword{As
    formas que o código é exibido ao usuário e que ele é salvo em disco são
    controladas por arquivos de configuração distintos. O arquivo `theme.ini'
    contém, entre outras configurações, informações de como serializar a árvore
    sintática.}}
    \end{citacao}
    \begin{citacao}
    The output format setting is given the same way, but in a separate file,
    called `output \_format.ini'. The decision of this separation was in view of
    teams of programmers who want to use a single convention for the saved
    files, but keep the display the choice of each. So members of this team can
    share their `output\_format.ini 'files while customizing the `theme.ini'
    file to their liking. \cite[our translation]{structuredEditorStudy}
    \footnote{\brazilword{A configuração de formato de saída é dada da mesma
    forma, mas em um arquivo separado, chamado `output\_format.ini'. A decisão
    desta separação foi em vista de equipes de programadores que queiram
    utilizar uma convenção única para os arquivos salvos, mas manter a exibição
    a escolha de cada um. Assim os integrantes desta equipe podem compartilhar
    os seus arquivos `output\_format.ini' enquanto personalizam o arquivo
    `theme.ini' a seu gosto.}}
    \end{citacao}

    Based on this, we may think about writing plugins for common text
    editors/IDEs as Sublime Text. So while loading files from the disk, such
    plugin calls the formatter and does the formatting according to the display
    settings for the user. After that, when the user saves the file, the file
    with the original formatting is returned.

    To assist in this process, an autoconfiguration module is a great help. It
    detects how the source code is formatted and creates configuration files for
    it. So when saving the file, the file is automatically saved in the
    formatting it was originally read from the file system. So we have the same
    benefit of structured editors as the proposed work of
    \textcite{structuredEditorStudy}. At first we can think with the following
    goal/idea for a new automated software tool:

    \medskip
    \begin{bluebox}
    \begin{enumerate}[nolistsep]
        \item Create an easy-to-configure and expandable formatter for the
        existing and coming up programming languages.
    \end{enumerate}
    \end{bluebox}

\subsection{Problem}

    The problem proposed to solve is the creation of a Universal Beautifier.
    Current softwares are limited to a similar/restricted set, or even a single
    language and in addition, many are limited in what they can do for you when
    processing/formatting/beautifying your source code.
    \cite{universalCodeFormatter}

    Below there are some basic formatting rules for illustration:

    \medskip
    \begin{bluebox}
    \begin{enumerate}[nosep,nolistsep]
        \item Add new lines after `\{' and before `\}
        \item Add new lines before `\{'
        \item Remove empty lines
        \item Add comment lines before function
        \item Add new lines after `;'
        \item Add new lines after `\}'
        \item Remove new lines
        \item Reduce whitespace
        \item Put the code again in the input box above after submit
    \end{enumerate}
    \end{bluebox}
    \vspace{-4mm}\begin{flushright}\textcite{prettyPrinter}\end{flushright}

    From this point, a sketch is presented on the problem, solutions,
    information as for why to want make such software, or even why do we want to
    beautifying things:

@@

        \item There are many different tools, sometimes paid, and difficult to
        complete. \cite{universalCodeFormatter}

        \item Many programming languages exist, so always having Beautifier
        software for each of them is very laborious
        \cite{universalCodeFormatter}. But the approach to a Universal
        Beautifier proposed in this work, would allow easily new languages to be
        added, being completely different from previous ones, or alike. And in
        case of similarities between them, it is enough to reuse their
        configuration structures already implemented.

        \item Looking for a Beautifier for each one of them because programmers
        currently work daily with several of these languages, and they are not
        similar. So you need to configure several beautifiers to do the
        formatting. This is a problem because only a few beautifiers are more
        complete, and every time you need to make a change in the formatting
        style, you must manually propagate the same change over several
        different program configuration files, which is bad because it takes the
        user a lot of time to learn how to handle many different types of
        settings. \cite{Schweitzer}

        \item In the case of ideal Beautifier, a change in your styling is
        propagated to all languages. And if you want to leave some language out
        of it, you just need to remove it from the list on which the
        configuration block applies to, and `a)' leave it out so no change is
        applied to. Or `b)' create a new block including only the block within
        the desired settings.

        \item
        \begin{citacao}
        % \setlength{\itemindent}{5pt}
        One of absolute worst, worst methods of teamicide for software developers is to engage
        in these kinds of passive-aggressive formatting wars. I know because I've been there.
        They destroy peer relationships, and depending on the type of formatting, can also damage
        your ability to effectively compare revisions in source control, which is really scary.
        I can't even imagine how bad it would get if the lead was guilty of this behavior. That's
        leading by example, all right. Bad example. \cite{Atwood}
        \end{citacao}

        \item
        \begin{citacao}
        So yes, absurd as it may sound, fighting over whitespace characters and other seemingly
        trivial issues of code layout is actually justified. Within reason of course -- when done
        openly, in a fair and concensus building way, and without stabbing your teammates in the
        face along the way. \cite{Atwood}
        \end{citacao}

        \item
        \begin{citacao}
        I'd say there are two main reasons to enforce a single code format in a project. First has
        to do with version control: with everybody formatting the code identically, all changes in
        the files are guaranteed to be meaningful. No more just adding or removing a space here or
        there, let alone reformatting an entire file as a `side effect' of actually changing just a
        line or two. \cite{Geukens}
        \end{citacao}

@@

\subsubsection{Ideas}

@@

    Ideas for implementation:

\medskip
\begin{bluebox}
\begin{enumerate}[leftmargin=*]

    \item Implement tabstops with white space align. The solution - move
    tabstops to fit the text between them and align them with matching tabstops
    on adjacent lines. \url{http://nickgravgaard.com/elastic-tabstops/}
    \url{https://forum.sublimetext.com/t/elastic-tabs/128}

\end{enumerate}
\end{bluebox}

@@

% How to add `parsep` to `itemsep` and set `parsep` to 0pt, when declaring my list?
% https://tex.stackexchange.com/questions/366904/how-to-add-parsep-to-itemsep-and-set-parsep-to-0pt-when-declaring-my-list
\begin{sloppypar}
\begin{bluebox}\RaggedRight
\begin{enumerate}[leftmargin=*,parsep=0pt]

    \item CodeBeautify is an online code beautifier which allows you to beautify
    your source code: \url{http://codebeautify.org/}.

    \item A universal code formatter, written in Dart:
    \url{https://pub.dartlang.org/packages/unifmt}.

    \item Google-java-format is a program that reformats Java source code to
    comply with Google Java Style:
    \url{https://github.com/google/google-java-format}.

    \item CodeFormatter is a Sublime Text 2/3 plugin that supports format
    (beautify) source code.
    \url{https://github.com/akalongman/sublimetext-codeformatter} and
    \url{https://github.com/aukaost/SublimePrettyYAML}

    \item UniversalIndentGUI offers a live preview for setting the parameters of
    nearly any indenter. You change the value of a parameter and directly see
    how your reformatted code will look like. Save your beauty looking code or
    create an anywhere usable batch/shell script to reformat whole directories
    or just one file even out of the editor of your choice that supports
    external tool calls: \url{http://universalindent.sourceforge.net/} and
    \url{https://github.com/danblakemore/universal-indent-gui}.

    \item Language-agnostic pretty-printing through machine learning (uh, like,
    is this possible? YES, apparently). By Terence Parr (primary developer),
    Fangzhou (Morgan) Zhang (help with initial development), Jurgen Vinju
    (co-author of academic paper, help with empirical results and algorithm
    discussions). \url{https://github.com/antlr/codebuff}

    \item To every developer in this world, the closest thing to their heart is
    the text editor of their choice. Over the last few years many new text
    editors has come into the market in both free and paid model, but
    unfortunately not all of them were able to make a real dent on the developer
    community. I remember in my college days we uses to use Notepad++ as our
    beloved text editor, as at that point of time it was one of the popular and
    free text editor with a lot of features for coding. But as time goes on, the
    entire development community started to lean towards sublime text since it’s
    launch.
    \url{https://www.isaumya.com/sublime-text-vs-atom-which-one-i-prefer-most-and-why/}

    \item As a developer, your code editor is one of the most important parts of
    your setup. It can save your wrists and fingers from repetitive strain
    injuries. It can save your eyes from going blind after a coding marathon.
    \url{https://hackernoon.com/virtualstudio-code-the-editor-i-didnt-think-i-needed-16970c8356d5}

    \item VS Code is an Editor while VS is an IDE.
    \url{https://stackoverflow.com/questions/30527522/what-are-the-differences-between-visual-studio-code-and-visual-studio}

    \item What is the difference between VS Code and VS Community?
    Visual Studio Code is a streamlined code editor with support for development operations like
    debugging, task running and version control. It aims to provide just the tools a developer needs
    for a quick code-build-debug cycle and leaves more complex workflows to fuller featured IDEs.
    For more details about the goals of VS Code, see Why VS Code.
    \url{https://code.visualstudio.com/docs/supporting/faq#_licensing}

    \item Reg Replace is a plugin for Sublime Text 2 that allows the creating of commands consisting of
    sequences of find and replace instructions.
    \url{https://forum.sublimetext.com/t/regreplace-plugin/3810}

    \item The main reason I moved was that I find that it’s much slower, the simple things like opening a
    new window for a project should be instantaneous and sadly it’s far from it. As I've said before
    it's all about personal preference, I've gone back to Sublime but Adam for example is sticking
    with it...
    \url{http://engageinteractive.co.uk/blog/atom-review}
